---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## 1.Loading and preprocessing the data

### 1.1.uzip the file

```{r,eval=T,echo=F}
setwd("D:\\Git\\RepData_PeerAssessment1\\")
```
### 1.2.read data
```{r,eval=T,echo=T}
if(!exists("activity.csv")){
      unzip(zipfile = "activity.zip") #uzip zip file   
}
dat=read.csv(file="activity.csv",header = T,sep = ",",
         stringsAsFactors = F) #read data
dat$date=as.POSIXct(dat$date) #change date colume type
str(dat)
head(dat)

```



## 2.What is mean total number of steps taken per day?

### 2.1 Calculate the total number of steps taken per day
```{r}
tmp=dat[complete.cases(dat),] #without NA

# Calculate the total number of steps taken per day
tapply(tmp$steps,tmp$date,sum)
```

### 2.2.  Make a histogram of the total number of steps taken each day
```{r,eval=T,echo=T}

#Make a histogram of the total number of steps taken each day
library(plyr) #load plyr
per_day_steps=ddply(.data = tmp,.variables = .(date),.fun = summarize,per_day_step=sum(steps))

#  Make a histogram of the total number of steps taken each day
library(ggplot2)
library(scales)

g=ggplot(data = per_day_steps,aes(x=date,y=per_day_step))
g+geom_histogram(stat="identity")


```

### 2.3.  Calculate and report the mean and median of the total number of steps taken per day
```{r}
#mean of the total number of steps taken per day
per_day_mean_steps=ddply(.data = tmp,.variables = .(date),.fun = summarize,per_day_step=mean(steps))
head(per_day_mean_steps)
#median of the total number of steps taken per day
per_day_median_steps=ddply(.data = tmp,.variables = .(date),.fun = summarize,per_day_step=median(steps))
head(per_day_median_steps)

```


## 3.What is the average daily activity pattern?

### 3.1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
df_interval=ddply(tmp,.(interval),summarize,mean_steps=mean(steps))
g1=ggplot(data = df_interval,aes(x=interval,y=mean_steps))
g1+geom_point()
```

### 3.2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
df_interval=ddply(tmp,.(interval),summarize,max_step=max(steps))
g2=ggplot(data = df_interval,aes(x=interval,y=max_step))
g2+geom_point()
#print the max one
df_interval[which.max(df_interval$max_step),]
```

## 4.Imputing missing values

### 4.1. the total number of rows with NAs  
the total number of rows with NAs`r nrow(dat)-nrow(tmp)`
```{r}
nrow(dat)-nrow(tmp)
```

### 4.2.  filling in all of the missing values in the dataset  
```{r}
dat[is.na(dat$steps),]$steps=median(tmp$steps)
new_dat=dat
```


### 4.3.   Calculate and report the mean and median total number of steps taken per day 
```{r}
total_steps=ddply(.data = new_dat,.variables = .(date),.fun = summarize,all_step=sum(steps))
#Make a histogram 

g4=ggplot(data = total_steps,aes(x=date,y=all_step))
g4+geom_histogram(stat="identity")


new_mean_steps=ddply(.data = new_dat,.variables = .(date),.fun = summarize,new_mean_step=mean(steps))
head(new_mean_steps)
#median of the total number of steps taken per day
new_median_steps=ddply(.data = new_dat,.variables = .(date),.fun = summarize,new_median_steps=median(steps))
head(new_mean_steps)

```



## 5.Are there differences in activity patterns between weekdays and weekends?

### 5.1 .Create a new factor variable in the dataset with two levels – “weekday” and “weekend” i
```{r,message=FALSE}
library(lubridate)
new_dat$wday=wday(new_dat$date)
bre=c(0,5,7)
new_dat$fact=cut(x = new_dat$wday,breaks = bre,labels = c("weekday","weekend"),include.lowest = F)
```


### 5.2. make plot
```{r}
intervals=ddply(.data = new_dat,.variables = .(fact,interval),.fun = summarize,median_steps=median(steps),mean_steps=mean(steps))
library(reshape2)
df_melt=melt(data = intervals,c("interval","fact"))
g5=ggplot(data = df_melt,aes(x=interval,y=value))
g5+geom_line()+facet_grid(. ~ fact)

```

